\documentclass[DIN, pagenumber=false, fontsize=11pt, parskip=half]{scrartcl}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[T1]{fontenc} 
\usepackage{commath}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{float}
\usepackage{tikz-timing}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{xstring}
\usepackage{circuitikz}
\usepackage{listings} % needed for the inclusion of source code
\usepackage[final]{pdfpages}
\usepackage{subcaption}
\usepackage{import}
\usepackage{cleveref}
\usepackage{bm}
\usepackage{tabularx}

\usetikzlibrary{calc,shapes.multipart,chains,arrows}

\newcommand{\Prb}[1]{P(\text{#1})}
\newcommand{\CPr}[2]{P(\text{#1}|\text{#2})}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\rank}{rank}
\newcommand{\R}[0]{\mathbb{R}}

%Inkscape fuckery
\newcommand{\incfig}[2][\columnwidth]{%
    \def\svgwidth{#1}
    \import{./}{#2.eps_tex}
}

\title{Pattern Recognition}
\author{Tim Luchterhand, Paul Nykiel, Jonas Strauch (Group P)}

\begin{document}
    \maketitle
    \section{Independent Component Analysis}
    See the file a1.py for the solution. Specify the the .wav files as program arguments.

    \section{Autoencoder}
    \begin{enumerate}
        \setcounter{enumi}{2}
        \item The data points are not bound to $[-1, 1]$. As $\tanh(x) \in [-1, 1]$ it would thus not be possible
            to reconstruct the data points with $\tanh$ as the transfer function in the output layer.

        \item The distribution of the data points can not be described by a straight line. Thus a linear
            model is insufficient to describe the data points. The non linear autoencoder is more expressive,
            it is able to describe non linear distributions.
            
            Thus the model is able to achieve a better reconstruction of the data points. And thus a higher entropy
            in the latent space, this results in a more balanced latent space.
    \end{enumerate}
\end{document}
